Light inextensible strings under tension in the Schwarzschild geometry

### 2018-10-01 string_microarticle.tex
replace diagram with the fixed_EH_intersection work

Figure~\ref{closest_approach_non_self_intersecting} shows non-self
intersecting strings indexed by minimum distance of approach to the
singularity, which is taken to occur at~$\phi=0$.  Strings with a
sufficiently close passage to the event horizon self-intersect
(Figure~\ref{closest_approach_self_intersecting}).  Numerical methods
show that the critical value is~$\simeq 1.076109317$, with an
uncertainty of~1 in the last digit: if the closest approach is less
than this value, the string crosses itself at~$\phi=\pi/2$.
Figure~\ref{one_free_end} shows some strings that are tangent to the
event horizon and pass through the point~$\left(2,0\right)$

@@

\begin{figure}[h!]
\centering
\includegraphics[width=70mm]{one_free_end_r_equals_2.pdf}
\caption{Strings arranged by angle made at $r=2$, one free end}
\label{one_free_end}
\end{figure}

@@

In Figure~\ref{closest_approach_non_self_intersecting}, one's
classical intuition would suggest that the black hole feels a force to
the left, and should start accelerating.  However, it is not clear by
what mechanism such a force would be transmitted: the situation is
steady, so no gravitational waves are produced; the string is
inextensible, so stores no energy.  Likewise,
Figure~\ref{one_free_end} would suggest that angular momentum is
transmitted to the black hole, but no mechanism is apparent.

>>>>

Figure~\ref{closest_approach_non_self_intersecting} shows non-self
intersecting strings indexed by minimum distance of approach to the
singularity, which is taken to occur at~$\phi=0$.  Strings with a
sufficiently close passage to the event horizon self-intersect
(Figure~\ref{closest_approach_self_intersecting}).  Numerical methods
show that the critical value is~$\simeq 1.076109317$, with an
uncertainty of~1 in the last digit: if the closest approach is less
than this value, the string crosses itself at~$\phi=\pi/2$.
Figure~\ref{fixed_EH_intersection} shows some strings that are tangent
to the event horizon at~$\phi=0$.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=70mm]{one_free_end_fixed_EH_intersection.pdf}
\caption{Strings tangential to event horizon}
\label{fixed_EH_intersection}
\end{figure}

@@

In Figure~\ref{closest_approach_non_self_intersecting}, one's
classical intuition would suggest that the black hole feels a force to
the left, and should start accelerating.  However, it is not clear by
what mechanism such a force would be transmitted: the situation is
steady, so no gravitational waves are produced; the string is
inextensible, so stores no energy.  Likewise,
Figure~\ref{fixed_EH_intersection} would suggest that angular momentum is
transmitted to the black hole, but no mechanism is apparent.
